Tree size, microhabitat, and hydraulic traits shape drought responses in a temperate broadleaf forest

### 2019-09-20 manuscript/climate_sensitivity_draft.Rmd
coded table 4

![Table 4 - individual variable tests](tables_figures/Table4.png) #this is tested_traits_all

>>>>

```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
hypothesis_table <- read.csv("tables_figures/univariate_models_table.csv", stringsAsFactors = FALSE, check.names = FALSE) #note: this table is a rearranged version of `tested_traits_best_coeff.csv`.
kable(hypothesis_table, booktabs = TRUE, caption = "**Table 4. Univariate models**", format = 'latex', escape = TRUE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 12, protect_latex = TRUE) %>%
  add_header_above(c(" "," "," ","all droughts"=2,"1966"=2, "1977" = 2, "1999" = 2)) %>%
  kable_styling()
```
